\LARGE \bf Enhancing Security in Multi-Robot Systems through Co-Observation Planning, Reachability Analysis, and Network Flow

### 2024-12-08 response.tex

\documentclass{article}
%% Language and font encodings
\input{preamble/common}
\usepackage[english]{babel}
\usepackage{times} % make the section title in Times New Roman

\usepackage{booktabs}
\usepackage{tabu}
\usepackage[T1]{fontenc}

%% Sets page size and margins
\usepackage[a4paper,top=2.5cm,bottom=2cm,left=1.7cm,right=1.7cm,marginparwidth=1.75cm]{geometry}

%% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
% \usepackage[colorlinks=true, allcolors=blue]{hyperref}
% \usepackage{indentfirst}
% \usepackage{graphicx}
% \usepackage{subfigure}
\usepackage{float}
\usepackage{threeparttable} 
\usepackage{multirow}
\usepackage{url}

@@

\vspace{0.2cm}
\noindent
First and foremost, we sincerely thank the Editor-in-Chief, Associate Editor, and anonymous reviewers for their insightful comments and suggestions. These have been carefully incorporated into the revised manuscript, resulting in a clearer, more informative, and more readable version. We acknowledge the reviewers' concerns regarding grammatical errors, unclear definitions, and poorly formatted figures, which were noted as obstacles to evaluating the paper's technical contributions. In this revision, we have thoroughly addressed these issues by eliminating grammatical errors, refining definitions and notations for clarity, and replotting the figures to enhance readability. All reviewer comments have been carefully addressed, and the corresponding changes have been highlighted in \new{blue} for ease of reference. Our detailed responses to the reviewers' comments, provided in a 1:1 correspondence, are outlined below.
\vspace{0.2cm}
\noindent
Yours sincerely,

%\vspace{0.2cm}
\noindent
Ziqi Yang, Roberto Tron

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Rewiewer 1
\newpage
\section{Response to reviewer 1}

%%%%%%%%%%%%% Comment 1.1
\begin{cmt*}{}{}

	This paper proposes a multi-agent mobile robot planning algorithm that
	is robust agains attackers that would compromise the agents by
	directing them to unsafe regions. This is achieved by incorporating 1)
	co-observation constraints so that the agents could watch over each
	other, 2) reachability constraints so that the region the agents could
	potentially enter does no overlap with unsafe regions, and 3) sub-team
	planning algorithm to improve robustness by adding more number of
	agents.

	The proposed method is interesting, but I think the writing must be
	improved significantly to secure the clarity, and there are a lot of
	grammar mistakes that need to be fixed. To me, it appears that the
	draft may have been prepared somewhat hastily, which is not considerate
	of the reviewers' time.

\end{cmt*}
\vspace{0.1cm}
\noindent
\underline{\textbf{Response:}}
\vspace{0.2cm}
We are grateful for your thoughtful comments and for expressing interest in our proposed method. We sincerely apologize for the grammatical mistakes in the initial submission and acknowledge the importance of presenting our work with clarity and professionalism. In the revised version, we have been extra careful to address all grammar issues and have implemented thorough proofreading to minimize similar mistakes in future submissions. We greatly appreciate your patience and constructive feedback, which have been invaluable in improving the quality of our manuscript.

@@

\vspace{0.3cm}

%%%%%%%%%%%%% Comment 1.0
\begin{cmt}{}{}        %% use * when do not need enumerate
	It seems like Example 1 is introduced as an example to help
	readers understand the formulation (1) in details. However, it is still
	vague, and it doesn't easily connect to Figure 3b.
\end{cmt}
\vspace{0.1cm}
\noindent
\underline{\textbf{Response:}}
\vspace{0.2cm}

\begin{example}\label{example:map_exploration}
	\new{Robots are tasked to navigate an unknown task space, collecting sensory data to reconstruct a field (see Fig. 2a). The space is modeled as grid points, each with an associated value. The goal is to find paths that minimize uncertainty in reconstructing the field. Each grid point $j$ is associated with a Kalman Filter (KF) [28] to track uncertainty through its covariance $P_j$, updated based on the measurements taken by robots along the trajectory $\vq$, where measurement quality, modeled by a Gaussian radial basis function, is higher near the robot. The optimization objective $\varPhi(\vq)=\max_j P_j(\vq)$ is to minimize the maximum uncertainty (detailed in [6]).}
\end{example}
\begin{figure}[h]
	\centering
	\subfloat[\new{Map exploration task.}\label{fig:illustration}]{\includegraphics[width = 0.45\linewidth]{illustration figure_1}} 
	\subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[width = 0.45\linewidth]{Grid_world}}
	\caption{\new{(a) Grid world example of a task planned in an $8 \times 8$ grid world. Blue grids are obstacles, orange and green grids are forbidden regions.}}
  \end{figure}
\vspace{0.3cm}

%%%%%%%%%%%%% Comment 1.2
\begin{cmt}{}{}
	Personally, I think to much space is dedicated to the details of how
	reachability constraints are implemented in the ADMM formulation (Sec.
	D, E, F, G, H). Although they are important details, I think this part
	can be condensed more, and some of the details can be deferred to the
	Appendix, so that some space can be dedicated more to improve the
	clarity of the other sections.
\end{cmt}
\vspace{0.1cm}
\noindent
\underline{\textbf{Response:}}
\vspace{0.2cm}

### 2024-12-08 paper.tex
writting response

\noindent\myparagraph{Related research} The trajectory planning problem of MRS remains as a subject of intense study for many decades, and optimization is a common approach in such area. Optimization-based approaches are customizable to a varity of constraints (e.g. speed limit, avoiding obstacles) and task specifications (e.g. maximum surveillance coverage, minimal energy cost). In contrast to our work in \Cref{sec:ADMM-planning}, many motion planning tasks require a non-convex constraint problem formulation, most contributors focused on convex problems, and only allow for a few types of pre-specified non-convex constraints through convexification\cite{liu2014solving}\cite{VanParys2016}\cite{Schulman2014}. Several optimization techniques like mixed integer programs with quadratic terms (MIQP)~\cite{mellinger2012mixed} and ADMM~\cite{bento2013message} have been used to reduce computational complexity and to incorporate more complex non-convex constraints.

Graph-based search is another extensively explored approach in trajectory planning problems, such as formation control \cite{tanner2004leader,hu2019distributed} and MAPF problems \cite{stern2019multi}. In traditional MAPF formulations, environments are abstracted as graphs, with nodes representing positions and edges denoting possible transitions between positions, and solved as a network flow problem \cite{yu2013multi,yu2016optimal}. This formulation allows for the application of combinatorial network flow algorithms and linear program techniques, offering efficient and more flexible solutions to the planning problem. %In contrast with such approach, our research in \Cref{sec:cross-trajectory} abstracts the existing Multi-Robot System (MRS) trajectory (instead of the environment) into a directed graph and formulates the cross-trajectory co-observation paths as flows.
% \rtron{Cite the paper from the reviewer, as well as the paper from Tedrake on the IRIS decomposition, saying that ellipsoids have been used to create approximations of the free configuration space, not to bound reacheability, and not for security application here.}

@@

{\news The rest of this paper is organized as follows. \Cref{sec:ADMM-planning} introduces the ADMM-based optimal trajectory solver and the security constraints. \Cref{sec:cross-trajectory} introduces the enhanced security planning algorithm through cross-trajectory co-observation. \Cref{sec:summary} concludes this article.

@@

\begin{example}\label{example:map_exploration}
\new{Robots are tasked to navigate an unknown task space, collecting sensory data to reconstruct a field (see~\Cref{fig:illustration}). The space is modeled as grid points, each with an associated value. The goal is to find paths that minimize uncertainty in reconstructing the field. Each grid point $j$ is associated with a Kalman Filter (KF) \cite{anderson2012optimal} to track uncertainty through its covariance $P_j$, updated based on the measurements taken by robots along the trajectory $\vq$, where measurement quality, modeled by a Gaussian radial basis function, is higher near the robot. The optimization objective $\varPhi(\vq)=\max_j P_j(\vq)$ is to minimize the maximum uncertainty (detailed in \cite{yang2020multi}).}

@@

\subsubsection{Alternating Directions Method of Multipliers (ADMM)}\label{chapter:ADMM review}
The basic idea of the ADMM-based solver introduced in \cite{yang2020multi} is to separate the constraints from the objective function using a different set of variables $\vz$, then solve separately in \eqref{eq:general-problem}.
More specifically, we rewrite the constraint $\vq\in\varOmega$ using an indicator function $\varTheta$ and include it in the objective function (details can be found in \cite{yang2020multi}). 
%In the traditional application of ADMM, the variables $\vz$ are simple duplicates of $\vx$ projected to the constraint set $\Omega$. However, in path planning problems, some constraints are non-convex, rendering the projection step more difficult (due to the presence of multiple local minima).
We allow $\vz = D(\vq)$ to replicate an arbitrary function of the main variables $\vq$ (instead of being an exact copy in general ADMM formulation), to transform constraint $\vq\in\Omega$ to $D(\vq) \in \sZ$ to allow for an easier projection step in \Cref{eq:z-update}. In summary, we transform \Cref{eq:general-problem} into
\begin{equation}\label{eq:ADMMSetConstraint_modified}
	\begin{aligned}
		&\max\quad \varPhi(\vq)+\varTheta(\vz), \\
		& \begin{array}{r@{\quad}c}
			s.t.& D(\vq)-\vz=0,
		\end{array} 
	\end{aligned}
\end{equation}
where $D(\vq)= [D_1(\vq)^T,\dots,D_l(\vq)^T]^T$ is a vertical concatenation of different functions for different constraints. This makes each constraint set $\mathcal{Z}_i$ independent and thus can be computed separately in later updating steps. $D_i(\vq)$ is chosen such that the new constraint set~$\cZ_i$ becomes simple to compute which is illustrated in later sections. % and the function~$D_i(\vq)$ can be used to select only the subset of the variables on which a constraint depends, speeding up computations.

@@

We now provide the functions $D(\vq)$, the sets $\cZ$, and the corresponding projection operators $\Pi_\cZ$ for security constraints including co-observation security constraints (\Cref{sec:co-observation-constraint}), and reachability constraints (\Cref{sec:ellipsoid-point}-\Cref{eq:region_ellipsoid_constraint}). The latter is based on the definition of \emph{ellipse-region-constraint} (\Cref{sec:reachability}).
Formulation of traditional path planning constraints like velocity constraints and convex obstacle constraints can be found in \cite{yang2020multi}, thus are omitted in this paper.

@@

\subsection{Co-observation schedule constraint}\label{sec:co-observation-constraint}
The co-observation constraint ensures that two robots come into close proximity at scheduled times to observe each other's behavior. This constraint is represented as a relative distance requirement between the two robots at a specific time instant, ensuring they are within a defined radius to inspect each other or exchange data. %Importantly, the co-observation locations must be chosen to guarantee that the ellipsoidal reachability regions, as discussed in \Cref{sec:reachability}, do not intersect with any forbidden regions.

@@

{\news The condition that a reachability ellipsoid $\cE(q_1,q_2)$ does not intersect with any forbidden region is sufficient to secure the trajectory of the robot between $q_1$ and $q_2$ according to \Cref{def:secured-plan}: any deviation to a point $p_o$ outside $\cE(q_1,q_2)$ will cause the robot to miss a potential observation at $p_2$, $t_2$. \Cref{def:secured-plan} can then be restated as follows:
\begin{definition}\label{rmk:revised-security}
  A multi-robot trajectory is secured against plan-deviation attacks if there exists a co-observation plan such that the reachability region between each consecutive co-observation does not intersect with any forbidden regions.
\end{definition}
}

\subsection{Transformation to canonical coordinates}\label{sec:rotation2Standard}
\newcommand{\oFE}{o}
{\news To use the definition of reachability ellipsoid from the section above as computational constraints for ADMM, we first apply a differentiable rigid body transformation to reposition the ellipse $\cE$ from the global frame $\cF$ to a canonical frame $\cF_\cE$, where the origin of $\cF_\cE$ is at the ellipsoid's center $\oFE = \frac{1}{2}(q_1+q_2)$, and the first axis of $\cF_\cE$ is aligned with the foci (see \Cref{fig:EllipseConstraintExample} for an illustration). 
From this definition, a unit vector along the first axis of the ellipsoid in the frames $\cF$ and $\cF_\cE$ is given by $\nu_\cF = \frac{q_2-q_1}{\norm{q_2-q_1}}$ and $\nu_\cE =[1,0,0]^T$, respectively.
The full transformation from coordinates $q^\cE\in\cF$ to $q\in\cF$, and its inverse, are then parametrized by a rotation $R^\cF_\cE$ and a translation $o^\cF_\cE$ as (we drop the subscript and superscript from $R^\cF_\cE$ and $o^\cF_\cE$ to simplify the notation):
\begin{equation}\label{eq:transformations}
  q=R\Eframe{q}+\oFE,\quad
  \Eframe{q}=R\transpose(q-\oFE).
\end{equation}
where the rotation matrix $R=H(\nu_\cF(q_1,q_2),\nu_\cE)$ is a \emph{Householder rotation} $H$ (a differentiable linear transformation describing the minimal rotation between the two vectors, see \cref{sec:householder} for details).  To simplify the notation, in the following, we will consider $H$ to be a function of $q_1,q_2$ directly, i.e. $H(q_1,q_2)$. More details on \eqref{eq:transformations} are given in \cref{apx:transformation}.
  % We define $\nu_\cF$ and $\nu_\cE$ to represent the $x$-axis unitary vector of $\cF_\cE$ in the frames $\cF$ and $\cF_\cE$, respectively. Formally:
  % \begin{align}
  %   \nu_\cF &= \frac{q_2-q_1}{\norm{q_2-q_1}}, & \nu_\cE&=[1,0,0]^T;
  % \end{align}
  % \new{see Fig.\ref{fig:EllipseConstraintExample} for an illustration. Note that $\nu_{\cF}$ is a function of $q_1,q_2$ while $\nu_\cE$ is constant. From the definition of $\cF_\cE$, the rotation $R$ can be found using a \emph{Householder rotation} (see \cref{sec:householder}), while from \eqref{eq:transformations} the translation $o$ must be equal to the center of $\cE(q_1,q_2)$ expressed in $\cF$, i.e.:}
  % \begin{align} 
  %   R&=H(\nu_\cF(q_1,q_2),\nu_\cE), &o&=\frac{1}{2}(q_1+q_2).
  % \end{align}

@@

  \begin{proposition}\label{prop:Ellipse2PointDiff}
    The differential of the projection operator $\pi_{p\cE}(q_{avoid}; q_1,q_2,a)$ with respect to the foci $q_1,q_2$ is given by the following (using $q$ as a shorthand notation for $q^\cE_{avoid}$)
    \begin{multline}
      \partial_{\left[\begin{smallmatrix}q_1\\q_2\end{smallmatrix}\right]} \pi_{p\cE}=-2 H [ SH(q-o)]_{\times}U   \\
      + \left( (q\transpose \partial_sQ' q)^{-1} H^{-1} Q' q q\transpose  (4Q' H[q - o]_\times U \right. \\
      \left.+ 2Q' H\partial_q o - \partial_b Q' q q \partial_q b) -  s H^{-1} S^2 \partial_b Q q \partial_q b\right) \\
      -2H^{-1} S H[q-o]_{\times} U  + (H^{-1}SH -I)\partial_q o.
    \end{multline}
  \end{proposition}
  \begin{proof}
  See \Cref{proof:Ellipse2PointDiff}.
  \end{proof}
  The differential of $D_p$ is the same as the one for $\pi_{p\cE}$.

@@

  \begin{proposition}\label{prop:dpi_ne_dt}
    The differential of the projection function $\pi^\cE_{\vn \cE}(\vq)$ with respect to the foci $q_1$ and $q_2$ is given by:
    \begin{equation}
      \partial_q \pi^\cE_{\vn \cE}(q) = \begin{cases}
        \partial_q p^\cE_{t1}-\partial_q p^\cE_{\cL} &  d_\cE \in [0, d_{\cE t}], \\
        \partial_q p^\cE_{t2}-\partial_q p^\cE_{\cL} &  d \in [- d_{\cE t},0), \\
        {0} & otherwise.
      \end{cases}
    \end{equation}
    where
    \begin{multline}
      \partial_q p_\cL =   (-\frac{d_{\cE t} n\transpose \partial_q o -2d_\cE \partial_q d_{\cE t}}{d_{\cE t}^3} )Q^{-1}n_\cE \\
      + \frac{d_\cE\partial_b Q^{-1} n_\cE \partial_q b -  2d_\cE Q^{-1}H[n]_\times U}{d_{\cE t}^2},
    \end{multline}
    \begin{equation}
      \partial_q p_{1} =  -\frac{Q^{-1}n_\cE \partial_q d_{\cE t} }{d_{\cE t}^2} 
      + \frac{\partial_b Q^{-1}n_\cE \partial_q b -  2Q^{-1}H[n]_\times U }{d_{\cE t}}.
    \end{equation}
  \end{proposition}
  \begin{proof}
  See \Cref{proof:dpi_ne_dt}.
  \end{proof}
 The differential of (\ref{eq:plane_ellipsoid_constraint}) can be written as:
  \begin{equation}
    \partial_q {D_{\vn\cE}} = -2 H \cross{\Eframe \Pi_{\vn \cE}}  M + H^{-1}\partial_q \Eframe \Pi_{\vn \cE}.
  \end{equation}
\subsection{Line-segment-ellipse reachability constraint}\label{chapter:ellipse to segment}
{\news As an intermediate step to consider polygon-shaped forbidden regions, the reachability constraint for hyperplane segments is studied.
For hyperplane $\Eframe \cL(\Eframe q) = \{ \Eframe q\in\mathbb{R}^m:  \vn_\cE\transpose \Eframe q = d_{\cE}\}$ with endpoints $\Eframe {p_1}$ and $\Eframe{p_2}$; this segment is defined as:}
\begin{equation}
\bmat{(\Eframe {p_1}- \Eframe{p_2})\transpose\\( \Eframe{p_2} - \Eframe{p_1})\transpose}  \Eframe p \leq \bmat{ \Eframe{p_2}\transpose\\- \Eframe{p_1}\transpose}( \Eframe{p_1}- \Eframe{p_2}), \quad \vn_\cE\transpose \Eframe q = d_{\cE}.
\end{equation}
When the \emph{tangent interpolation point} $\Eframe{p_{\cL}}$ stays within the segment (i.e. red region in \cref{fig:Ellipse-to-safezone}), the constraint is a plane-ellipse constraint in \cref{sec:ellipsoide-plane}. Otherwise (i.e. brown region in \cref{fig:Ellipse-to-safezone}), the constraint is a point-ellipse constraint in \cref{sec:ellipsoid-point}.

@@

We test the newly introduced security constraints with~\cref{example:map_exploration}, illustrated in~\cref{fig:example-application} in both simulations and on an experimental testbed, involving a 3-robot system assigned to explore a $10m\times10m$ region with one obstacle, \emph{Zone 1}, and two forbidden zones, \emph{Zone 2} and \emph{Zone 3}. The maximum velocity constraint $v_{max}=0.5m/dt$, time horizon $T=20$. %All robots are tasked with collecting sensor information on the vector field, with higher accuracy of sensor data for locations closer to the agent. %robots are expected to follow a boustrophedon pattern (similar to the unconstrained result in Figure~\ref{fig:SecurityBreak}). %We apply the new security constraints on the map exploration problem shown in \Cref{fig:example-application}, test the algorithm in both simulations and an experimental testbed. The 3-robot system is tasked to explore a $10m\times10m$ region with two forbidden regions \emph{Zone 2, 3}. The maximum velocity constraint $v_{max}$ is set to~$0.5m/dt$ a time limit of 20.

@@

%As depicted in Fig.\ref{fig:Grid-example-application}, no explicit tasks are assigned besides the start and goal locations. Agents 1 and 2 need to meet at times 8 and 14, while agents 2 and 3 need to meet at time 18. This result serves as the initial trajectory input for the ADMM solver. Considering this schedule, reachability for all agents in-between scheduled co-observations is constrained and kept away from the forbidden regions. % It's important to note that additional checkpoints (e.g., stationary security cameras) need to be incorporated to generate an attack-proof solution. Further solutions to avoid these checkpoints are discussed in \Cref{sec:cross-trajectory}.

@@

Our objective here is to ascertain the existence of feasible paths instead of optimizing specific tasks. While the ADMM-based solver \Cref{sec:ADMM-planning} presented earlier offers a broader range of constraint handling, RRT*'s efficient exploration of the solution space, coupled with its ability to incorporate obstacle constraints, makes it a fitting choice for building the checkpoint graph.

>>>>

\noindent\myparagraph{Related research} The trajectory planning problem of MRS remains as a subject of intense study for many decades, and optimization is a common approach in such area. Optimization-based approaches are customizable to a varity of constraints (e.g. speed limit, avoiding obstacles) and task specifications (e.g. maximum surveillance coverage, minimal energy cost). In contrast to our work in \cref{sec:ADMM-planning}, many motion planning tasks require a non-convex constraint problem formulation, most contributors focused on convex problems, and only allow for a few types of pre-specified non-convex constraints through convexification\cite{liu2014solving}\cite{VanParys2016}\cite{Schulman2014}. Several optimization techniques like mixed integer programs with quadratic terms (MIQP)~\cite{mellinger2012mixed} and ADMM~\cite{bento2013message} have been used to reduce computational complexity and to incorporate more complex non-convex constraints.

Graph-based search is another extensively explored approach in trajectory planning problems, such as formation control \cite{tanner2004leader,hu2019distributed} and MAPF problems \cite{stern2019multi}. In traditional MAPF formulations, environments are abstracted as graphs, with nodes representing positions and edges denoting possible transitions between positions, and solved as a network flow problem \cite{yu2013multi,yu2016optimal}. This formulation allows for the application of combinatorial network flow algorithms and linear program techniques, offering efficient and more flexible solutions to the planning problem. %In contrast with such approach, our research in \cref{sec:cross-trajectory} abstracts the existing Multi-Robot System (MRS) trajectory (instead of the environment) into a directed graph and formulates the cross-trajectory co-observation paths as flows.
% \rtron{Cite the paper from the reviewer, as well as the paper from Tedrake on the IRIS decomposition, saying that ellipsoids have been used to create approximations of the free configuration space, not to bound reacheability, and not for security application here.}

@@

{\news The rest of this paper is organized as follows. \cref{sec:ADMM-planning} introduces the ADMM-based optimal trajectory solver and the security constraints. \cref{sec:cross-trajectory} introduces the enhanced security planning algorithm through cross-trajectory co-observation. \cref{sec:summary} concludes this article.

@@

\begin{example}\label{example:map_exploration}
\new{Robots are tasked to navigate an unknown task space, collecting sensory data to reconstruct a field (see~\cref{fig:illustration}). The space is modeled as grid points, each with an associated value. The goal is to find paths that minimize uncertainty in reconstructing the field. Each grid point $j$ is associated with a Kalman Filter (KF) \cite{anderson2012optimal} to track uncertainty through its covariance $P_j$, updated based on the measurements taken by robots along the trajectory $\vq$, where measurement quality, modeled by a Gaussian radial basis function, is higher near the robot. The optimization objective $\varPhi(\vq)=\max_j P_j(\vq)$ is to minimize the maximum uncertainty (detailed in \cite{yang2020multi}).}

@@

\subsubsection{Alternating Directions Method of Multipliers (ADMM)}\label{chapter:ADMM review}
The basic idea of the ADMM-based solver introduced in \cite{yang2020multi} is to separate the constraints from the objective function using a different set of variables $\vz$, then solve separately in \eqref{eq:general-problem}.
More specifically, we rewrite the constraint $\vq\in\varOmega$ using an indicator function $\varTheta$ and include it in the objective function (details can be found in \cite{yang2020multi}). 
%In the traditional application of ADMM, the variables $\vz$ are simple duplicates of $\vx$ projected to the constraint set $\Omega$. However, in path planning problems, some constraints are non-convex, rendering the projection step more difficult (due to the presence of multiple local minima).
We allow $\vz = D(\vq)$ to replicate an arbitrary function of the main variables $\vq$ (instead of being an exact copy in general ADMM formulation), to transform constraint $\vq\in\Omega$ to $D(\vq) \in \sZ$ to allow for an easier projection step in \cref{eq:z-update}. In summary, we transform \cref{eq:general-problem} into
\begin{equation}\label{eq:ADMMSetConstraint_modified}
	\begin{aligned}
		&\max\quad \varPhi(\vq)+\varTheta(\vz), \\
		& \begin{array}{r@{\quad}c}
			s.t.& D(\vq)-\vz=0,
		\end{array} 
	\end{aligned}
\end{equation}
where $D(\vq)= [D_1(\vq)^T,\dots,D_l(\vq)^T]^T$ is a vertical concatenation of different functions for different constraints. This makes each constraint set $\mathcal{Z}_i$ independent and thus can be computed separately in later updating steps. $D_i(\vq)$ is chosen such that the new constraint set~$\cZ_i$ becomes simple to compute which is illustrated in later sections. % and the function~$D_i(\vq)$ can be used to select only the subset of the variables on which a constraint depends, speeding up computations.

@@

We now provide the functions $D(\vq)$, the sets $\cZ$, and the corresponding projection operators $\Pi_\cZ$ for security constraints including co-observation security constraints (\cref{sec:co-observation-constraint}), and reachability constraints (\cref{sec:ellipsoid-point}-\cref{eq:region_ellipsoid_constraint}). The latter is based on the definition of \emph{ellipse-region-constraint} (\cref{sec:reachability}).
Formulation of traditional path planning constraints like velocity constraints and convex obstacle constraints can be found in \cite{yang2020multi}, thus are omitted in this paper.

@@

\subsection{Co-observation schedule constraint}\label{sec:co-observation-constraint}
The co-observation constraint ensures that two robots come into close proximity at scheduled times to observe each other's behavior. This constraint is represented as a relative distance requirement between the two robots at a specific time instant, ensuring they are within a defined radius to inspect each other or exchange data. %Importantly, the co-observation locations must be chosen to guarantee that the ellipsoidal reachability regions, as discussed in \cref{sec:reachability}, do not intersect with any forbidden regions.

@@

{\news The condition that a reachability ellipsoid $\cE(q_1,q_2)$ does not intersect with any forbidden region is sufficient to secure the trajectory of the robot between $q_1$ and $q_2$ according to \cref{def:secured-plan}: any deviation to a point $p_o$ outside $\cE(q_1,q_2)$ will cause the robot to miss a potential observation at $p_2$, $t_2$. \cref{def:secured-plan} can then be restated as follows:
\begin{definition}\label{rmk:revised-security}
  A multi-robot trajectory is secured against plan-deviation attacks if there exists a co-observation plan such that the reachability region between each consecutive co-observation does not intersect with any forbidden regions.
\end{definition}
}

\subsection{Transformation to canonical coordinates}\label{sec:rotation2Standard}
\newcommand{\oFE}{o}
{\news To use the definition of reachability ellipsoid from the section above as computational constraints for ADMM, we first apply a differentiable rigid body transformation to reposition the ellipse $\cE$ from the global frame $\cF$ to a canonical frame $\cF_\cE$, where the origin of $\cF_\cE$ is at the ellipsoid's center $\oFE = \frac{1}{2}(q_1+q_2)$, and the first axis of $\cF_\cE$ is aligned with the foci (see \cref{fig:EllipseConstraintExample} for an illustration). 
From this definition, a unit vector along the first axis of the ellipsoid in the frames $\cF$ and $\cF_\cE$ is given by $\nu_\cF = \frac{q_2-q_1}{\norm{q_2-q_1}}$ and $\nu_\cE =[1,0,0]^T$, respectively.
The full transformation from coordinates $q^\cE\in\cF$ to $q\in\cF$, and its inverse, are then parametrized by a rotation $R^\cF_\cE$ and a translation $o^\cF_\cE$ as (we drop the subscript and superscript from $R^\cF_\cE$ and $o^\cF_\cE$ to simplify the notation):
\begin{equation}\label{eq:transformations}
  q=R\Eframe{q}+\oFE,\quad
  \Eframe{q}=R\transpose(q-\oFE).
\end{equation}
where the rotation matrix $R=H(\nu_\cF(q_1,q_2),\nu_\cE)$ is a \emph{Householder rotation} $H$ (a differentiable linear transformation describing the minimal rotation between the two vectors, see \cref{sec:householder} for details).  To simplify the notation, in the following, we will consider $H$ to be a function of $q_1,q_2$ directly, i.e. $H(q_1,q_2)$. More details on \eqref{eq:transformations} are given in \cref{apx:transformation}.
  % We define $\nu_\cF$ and $\nu_\cE$ to represent the $x$-axis unitary vector of $\cF_\cE$ in the frames $\cF$ and $\cF_\cE$, respectively. Formally:
  % \begin{align}
  %   \nu_\cF &= \frac{q_2-q_1}{\norm{q_2-q_1}}, & \nu_\cE&=[1,0,0]^T;
  % \end{align}
  % \new{see Fig.\ref{fig:EllipseConstraintExample} for an illustration. Note that $\nu_{\cF}$ is a function of $q_1,q_2$ while $\nu_\cE$ is constant. From the definition of $\cF_\cE$, the rotation $R$ can be found using a \emph{Householder rotation} (see \cref{sec:householder}), while from \eqref{eq:transformations} the translation $o$ must be equal to the center of $\cE(q_1,q_2)$ expressed in $\cF$, i.e.:}
  % \begin{align} 
  %   R&=H(\nu_\cF(q_1,q_2),\nu_\cE), &o&=\frac{1}{2}(q_1+q_2).
  % \end{align}

@@

  \begin{proposition}\label{prop:Ellipse2PointDiff}
    The differential of the projection operator $\pi_{p\cE}(q_{avoid}; q_1,q_2,a)$ with respect to the foci $q_1,q_2$ is given by the following (using $q$ as a shorthand notation for $q^\cE_{avoid}$)
    \begin{multline}
      \partial_{\left[\begin{smallmatrix}q_1\\q_2\end{smallmatrix}\right]} \pi_{p\cE}=-2 H [ SH(q-o)]_{\times}U   \\
      + \left( (q\transpose \partial_sQ' q)^{-1} H^{-1} Q' q q\transpose  (4Q' H[q - o]_\times U \right. \\
      \left.+ 2Q' H\partial_q o - \partial_b Q' q q \partial_q b) -  s H^{-1} S^2 \partial_b Q q \partial_q b\right) \\
      -2H^{-1} S H[q-o]_{\times} U  + (H^{-1}SH -I)\partial_q o.
    \end{multline}
  \end{proposition}
  \begin{proof}
  See \cref{proof:Ellipse2PointDiff}.
  \end{proof}
  The differential of $D_p$ is the same as the one for $\pi_{p\cE}$.

@@

  \begin{proposition}\label{prop:dpi_ne_dt}
    The differential of the projection function $\pi^\cE_{\vn \cE}(\vq)$ with respect to the foci $q_1$ and $q_2$ is given by:
    \begin{equation}
      \partial_q \pi^\cE_{\vn \cE}(q) = \begin{cases}
        \partial_q p^\cE_{t1}-\partial_q p^\cE_{\cL} &  d_\cE \in [0, d_{\cE t}], \\
        \partial_q p^\cE_{t2}-\partial_q p^\cE_{\cL} &  d \in [- d_{\cE t},0), \\
        {0} & otherwise.
      \end{cases}
    \end{equation}
    where
    \begin{multline}
      \partial_q p_\cL =   (-\frac{d_{\cE t} n\transpose \partial_q o -2d_\cE \partial_q d_{\cE t}}{d_{\cE t}^3} )Q^{-1}n_\cE \\
      + \frac{d_\cE\partial_b Q^{-1} n_\cE \partial_q b -  2d_\cE Q^{-1}H[n]_\times U}{d_{\cE t}^2},
    \end{multline}
    \begin{equation}
      \partial_q p_{1} =  -\frac{Q^{-1}n_\cE \partial_q d_{\cE t} }{d_{\cE t}^2} 
      + \frac{\partial_b Q^{-1}n_\cE \partial_q b -  2Q^{-1}H[n]_\times U }{d_{\cE t}}.
    \end{equation}
  \end{proposition}
  \begin{proof}
  See \cref{proof:dpi_ne_dt}.
  \end{proof}
 The differential of (\ref{eq:plane_ellipsoid_constraint}) can be written as:
  \begin{equation}
    \partial_q {D_{\vn\cE}} = -2 H \cross{\Eframe \Pi_{\vn \cE}}  M + H^{-1}\partial_q \Eframe \Pi_{\vn \cE}.
  \end{equation}
\subsection{Line-segment-ellipse reachability constraint}\label{chapter:ellipse to segment}
{\news As an intermediate step to consider polygon-shaped forbidden regions, the reachability constraint for hyperplane segments is studied.
For hyperplane $\Eframe \cL(\Eframe q) = \{ \Eframe q\in\mathbb{R}^m:  \vn_\cE\transpose \Eframe q = d_{\cE}\}$ with endpoints $\Eframe {p_1}$ and $\Eframe{p_2}$; this segment is defined as:}
\begin{equation}
\bmat{(\Eframe {p_1}- \Eframe{p_2})\transpose\\( \Eframe{p_2} - \Eframe{p_1})\transpose}  \Eframe p \leq \bmat{ \Eframe{p_2}\transpose\\- \Eframe{p_1}\transpose}( \Eframe{p_1}- \Eframe{p_2}), \quad \vn_\cE\transpose \Eframe q = d_{\cE}.
\end{equation}
When the \emph{tangent interpolation point} $\Eframe{p_{\cL}}$ stays within the segment (i.e. red region in \cref{fig:Ellipse-to-safezone}), the constraint is a plane-ellipse constraint in \cref{sec:ellipsoide-plane}. Otherwise (i.e. brown region in \cref{fig:Ellipse-to-safezone}), the constraint is a point-ellipse constraint in \cref{sec:ellipsoid-point}.

@@

We test the newly introduced security constraints with~\cref{example:map_exploration}, illustrated in~\cref{fig:example-application} in both simulations and on an experimental testbed, involving a 3-robot system assigned to explore a $10m\times10m$ region with one obstacle, \emph{Zone 1}, and two forbidden zones, \emph{Zone 2} and \emph{Zone 3}. The maximum velocity constraint $v_{max}=0.5m/dt$, time horizon $T=20$. %All robots are tasked with collecting sensor information on the vector field, with higher accuracy of sensor data for locations closer to the agent. %robots are expected to follow a boustrophedon pattern (similar to the unconstrained result in Figure~\ref{fig:SecurityBreak}). %We apply the new security constraints on the map exploration problem shown in \cref{fig:example-application}, test the algorithm in both simulations and an experimental testbed. The 3-robot system is tasked to explore a $10m\times10m$ region with two forbidden regions \emph{Zone 2, 3}. The maximum velocity constraint $v_{max}$ is set to~$0.5m/dt$ a time limit of 20.

@@

%As depicted in Fig.\ref{fig:Grid-example-application}, no explicit tasks are assigned besides the start and goal locations. Agents 1 and 2 need to meet at times 8 and 14, while agents 2 and 3 need to meet at time 18. This result serves as the initial trajectory input for the ADMM solver. Considering this schedule, reachability for all agents in-between scheduled co-observations is constrained and kept away from the forbidden regions. % It's important to note that additional checkpoints (e.g., stationary security cameras) need to be incorporated to generate an attack-proof solution. Further solutions to avoid these checkpoints are discussed in \cref{sec:cross-trajectory}.

@@

Our objective here is to ascertain the existence of feasible paths instead of optimizing specific tasks. While the ADMM-based solver \cref{sec:ADMM-planning} presented earlier offers a broader range of constraint handling, RRT*'s efficient exploration of the solution space, coupled with its ability to incorporate obstacle constraints, makes it a fitting choice for building the checkpoint graph.
